The effect of detector nonlinearity on \wfa\ PSF profiles for weak gravitational lensing measurements

### 2016-04-19 bias_from_NL.tex
Added derivation of beta from pixel model

An ideal detector would produce a measurable signal that is proportional to the detected photons. However, there are several places in the signal chain where this expected linearity is not realized, and the conversion of charge to measured voltage (or digital numbers) becomes non-linear. First of all, the charge accumulation rate might be a function of the photon-accumulation rate. This type of effect is known as reciprocity failure (RF), and it is a flux-dependent type of nonlinearity (\citealt{smith08}, \citealt{biesiadzinski11}). In addition to RF, the p-n junction acts as a parallel-plate capacitor, and as charge accumulates the depletion region narrows, causing a deviation from linearity of the charge-to-voltage conversion relation. Nonlinearity can also be introduced through the electronic gain of the ROIC. 
The last two types of nonlinearity depend on fluence (total flux per pixel, or integrated signal, as opposed to RF, which is flux dependent), and can be analyzed together in a singe transfer function typically called ``nonlinearity" (NL). We study the impacts of NL (more relevant at high signals) on PSF measurements in this paper, while we leave investigations on the consequences of RF (relevant at lower signals) on WL measurements for future work.

@@

To obtain a functional model of NL as a function of signal, we use laboratory measurements\footnote{Performed at Caltech by R. Smith and collaborators.} of H2RG 1.7 $\mu$m cutoff detectors, which have the same basic design of the H4RG that will be used in the WFI but with 18 $\mu$m pixels. A constant flux source is illuminated on the detector, and the NL measurements are done by non-destructive sample-up-the-ramp (SUTR) readout at multiple times. The value of the first frame is subtracted, and then the \emph{mean} signal is fitted to a polynomial. These measurements show that the voltage relation for a measured signal $S$ is well fit by a quadratic function in the mean signal $\langle Q \rangle$ of the form:
\begin{align}
S(Q)= Q + \beta Q ^2  (\mathrm{e^-})
\label{NL}
\end{align}

>>>>

An ideal detector would produce a measurable signal that is proportional to the detected photons. However, there are several places in the signal chain where this expected linearity is not realized, and the conversion of charge to measured voltage (or digital numbers) becomes non-linear. First of all, the charge accumulation rate might be a function of the photon-accumulation rate. This type of effect is known as reciprocity failure (RF), and it is a flux-dependent type of nonlinearity (\citealt{smith08}, \citealt{biesiadzinski11}). In addition to RF, each pixel's p-n junction acts as a parallel-plate capacitor, and as charge accumulates the depletion region narrows, causing a deviation from linearity of the charge-to-voltage conversion relation. Nonlinearity can also be introduced through the electronic gain of the ROIC. 
The last two types of nonlinearity depend on fluence (total flux per pixel, or integrated signal, as opposed to RF, which is flux dependent), and can be analyzed together in a singe transfer function typically called ``nonlinearity" (NL). We study the impacts of NL (more relevant at high signals) on PSF measurements in this paper, while we leave investigations on the consequences of RF (relevant at lower signals) on WL measurements for future work.

Assuming that the dominant contribution to nonlinearity is the varying capacitance of the pixel p-n junction, the correction to the detector signal is well approximated by a quadratic term:
\begin{align} \label{eq:defbeta}
S(Q)= Q + \beta Q ^2 % (\mathrm{e^-})
\label{NL}
\end{align}
Here, $Q$ is the true number of elementary charges collected in the pixel, $S$ is the number inferred from the voltage change at the sense node, and $\beta$ is a constant.  To estimate $\beta$, we compute $Q(V)=C(V)*V/q_e$, where the total capacitance is given by the varying junction capacitance plus a constant $C(V) = C_{\rm jn}(V) + C_{\rm fix}$. \textbf{[CITE McCAUGHREAN]}  The junction capacitance varies as
\begin{equation}
C_{\rm jn}(V) \sim (1+V/V_{bi})^{-1/2}
\end{equation}
Here, $V_{bi}$ is the ``built in'' potential of the junction and $V=V_{\rm DSUB}-V_{\rm RESET}+\delta V$, where $V_{\rm DSUB}$ is the constant potential at the diode cathode, $V_{\rm RESET}$ is the initial potential at the anode, and $\delta V$ is the change in anode potential due to accumulated photocharge.  As an example, we plug in measurements of a 2.4$\mu$m cutoff H2RG by Finger (2006): \textbf{[CITE FINGER]}% https://www.eso.org/sci/meetings/2006/neon-2006/Finger.pdf
\begin{eqnarray*}
V_{\rm bi} &=& 0.412{\mbox V} \\
V_{\rm DSUB} &=& 1{\mbox V} \\
V_{\rm RESET} &=& 0.5{\mbox V} \\
C_{\rm fix} &=& 17.8 {\mbox fF} \\
C_{\rm jn}(V=.912{\mbox V}) &=& 30 {\mbox fF}
\end{eqnarray*}¥
Using these parameters to compute $Q(V)$ for $ 0\le \delta V \le 0.3$ V (corresponding to maximum $Q$=60115) and then inverting to find $S(Q)$, we find it is well-fit (to 0.1\% or better) by (\ref{eq:defbeta}) with $\beta$=-1.18e-6.  In practice, HxRG calibrations have included additional polynomial parameters to reduce residuals, extend the range of valid $Q$, and account for additional nonlinear effects \textbf[CITE HILBERT PAPERS]; however, the additional parameters are highly degenerate, resulting in large variances in the fitted values.  For our purposes, it suffices to analyze the shape-distorting effects of nonlinearity using a single parameter, $\beta$, which encapsulates most of the effect.

@@

%To obtain a functional model of NL as a function of signal, we use laboratory measurements\footnote{Performed at Caltech by R. Smith and collaborators.} of H2RG 1.7 $\mu$m cutoff detectors, which have the same basic design of the H4RG that will be used in the WFI but with 18 $\mu$m pixels. A constant flux source is illuminated on the detector, and the NL measurements are done by non-destructive sample-up-the-ramp (SUTR) readout at multiple times. The value of the first frame is subtracted, and then the \emph{mean} signal is fitted to a polynomial. These measurements show that the voltage relation for a measured signal $S$ is well fit by a quadratic function in the mean signal $\langle Q \rangle$ of the form:
